### 2012-12-04 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
example c0_30 from farm (images)

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/")
```

```{r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
c2 <- seq(0, 20, length.out = 40)
```

@@

```{r }
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r}
as.table(apples)
```

``` {r }
p0
```

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/", fig.path="figure/c30-")
```

```{r}
price = 1
c0 = 30
c1 = 0
```

@@

```{r }
apples_plot
````

```{r}
apples
```
